%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% \iffalse %%%%
%                                                                              %
%  Copyright (c) 2014 - Michiel Helvensteijn   (www.mhelvens.net)              %
%                                                                              %
%  Please don't modify and distribute the LaTeX code of my personal CV.        %
%  The cv.tex file and the rubric files are not released under an open         %
%  source license. That's only the my-cv.cls and my-whenprinting.sty files.    %
%                                                                              %
%  I include these files merely as a usage example.                            %
%                                                                              %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% \fi %%%%

%\newcommand\loc[1]{ ~~--~~#1}

\begin{rubric}{Short-Term Programs and Conferences}
	\in*{2018}
		Computing in the 21th Century Conferences \& MSRA Faculty Submmit: Listen to speeches, keynote talks, and panels of many giants in the computer science. Topics varies from aritificial intelligence, machine learning, visual computing to quantum computing. I learned much from them such as Satya Nadella, Raj Reddy, Chi-Chih Yao, Jogn Hopcroft, Yoshua Bengio, Lenore Blum, Butler Lampson, and etc.
		\hfill\www{https://www.microsoft.com/en-us/research/event/computing-in-the-21st-century-conference-asia-faculty-summit-on-msras-20th-anniversary/}
    \in*{2017}
        \emph{Building Bridges} Education Support Program: Building Bridges is a Yale University organization. It takes a select group students from HKU, PKU, SJTU and Yale to teach middle schoolers in rural Shanxi Province. As a leader of SJTU team, I was in charge of the connection and arrangement of the members. Certificated by the Aixin Foundation Inc. of the United States. 
        \hfill\www{https://news.yale.edu/2017/10/31/building-bridges-tackles-educational-inequality-between-rural-urban-china}
    \in*{2017}
    	\emph{Tsinghua University} Summer Camp: Nano-OptoElectronics Lab, Department of Electronic Engineering, Tsinghua University.
    	\hfill\www{http://www.tsinghua.edu.cn/publish/thu2018en/index.html}
	\in*{2016}
		\emph{Top China} Summer Program: Together with the PKU, we organized the lectures, tours and other activities for students and professors from Brazil on the subject of "Buliding an Inclusive Society and Our Responsibility". As one of the leaders, I was in charge of the connection and arrangement. Certificated by the International Student Center of SJTU.
		\hfill\www{https://www.univali.br/intercambio/top-china/Paginas/default.aspx}


		
\end{rubric}
